SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/introdefhistory.tex
Link to more in structure

As such, the following serves to tie the published papers into a
whole, provide an overarching rationale and problem statements,
overview of the contributions and a discussion of the problematic
sides of the study seen from a philosophy of science viewpoint. It is
structured as follows: Section~\ref{sec:nodef} discusses the
possibility of defining the Semantic Web,
Section~\ref{sec:objectivity} discusses the problem of maintaining
objectivity, Section~\ref{sec:history} attempts to satisfy the
previous discussion by detailing the author's personal involvement in
the Semantic Web. Section~\ref{sec:motivation} has an overview of the
motivation behind this work.  Section~\ref{sec:related} puts the
present work into the context within the existing
literature. Section~\ref{sec:problems} summarises important research
problems and details the motivation, and
Section~\ref{sec:papersincontext} details how the contributions
address these problems and discusses weaknesses of the papers with the
benefit of hindsight. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}

>>>>

As such, the following serves to tie the published papers into a
whole, provide an overarching rationale and problem statements,
overview of the contributions and a discussion of the problematic
sides of the study seen from a philosophy of science viewpoint. It is
structured as follows: Section~\ref{sec:nodef} discusses the
possibility of defining the Semantic Web,
Section~\ref{sec:objectivity} discusses the problem of maintaining
objectivity, Section~\ref{sec:history} attempts to satisfy the
previous discussion by detailing the author's personal involvement in
the Semantic Web. Section~\ref{sec:motivation} has an overview of the
motivation behind this work.  Section~\ref{sec:prelims} provides some
further technical details and Section~\ref{sec:related} puts the
present work into the context within the existing
literature. Section~\ref{sec:problems} summarises important research
problems and details the motivation.
Sections~\ref{sec:papersincontext}~and~\ref{sec:unpublished} details
how the contributions address these problems and discusses weaknesses
of the papers with the benefit of hindsight. Future work is discussed
in Section~\ref{sec:future}. Key insights are finally summarised in
Section~\ref{sec:conclusions}.\todo{Big problem statement here}
